---
title: "Practice RMarkdown"
author: "abayard"
date: "2023-02-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
```

## Intro

#### This data set contains North Pole Environmental Observatory Bottle Chemistry data; including: Niskin bottle samples for measurements of salinity, oxygen isotopes composition, total alkalinity, and concentrations of phosphate, silicic acid, nitrate, nitrite, ammonium, and barium

#### Here is the data [link](https://arcticdata.io/catalog/view/doi:10.18739/A25T3FZ8X)

### Read data
```{r}
bg_chem <- read_csv("data/BGchem2008data.csv")
```
```{r}
colnames(bg_chem)

str(bg_chem)

head(bg_chem)
```

## Analysis

### Calc summary stats

```{r stats}
nitrate <- mean(bg_chem$NO3)
nitrite <- mean(bg_chem$NO2)
amm <- mean(bg_chem$NH4)
phos <- mean(bg_chem$P)
```


### calculate mean Redfield ratio

```{r ratio}
ratio <- (nitrate + nitrite + amm)/phos
```

The Redfield ratio in this data set is approx.

### Plot Redfield ratio

```{r plot, echo=FALSE}
plot(bg_chem$P, bg_chem$NO2 + bg_chem$NO3 + bg_chem$NH4)
```

